---
output: 
    html_document:
      code_folding: show
      highlight: haddock
      theme: spacelab
---


### Before the RMarkdown workshop on May 11th, 2016, please do the following:

> 1. Open up **RStudio**.  

> 2. Install and download the **devtools** R package by running the following in the R console. 

```{r devtools, eval = FALSE}
install.packages("devtools") # To include the session information
library("devtools") # To include the session information  
```

> 3. Check that you have the correct versions of **R** and **RStudio** by running `devtools::session_info()` in the R console.  

Here, `devtools::` tells **R** to use the `session_info()` function within the **devtools** package rather than the `sessionInfo()` function within the **utils** package.  Running `devtools::session_info()` allows us to see the version of **R** and **RStudio**. 

Do you have the following versions of **R** and **RStudio**?  

- **R:** `Version 3.3.0 (2016-05-03)`  
- **RStudio:** `0.99.1172`  

  - If you **do** then you are good to go!  
  - If you **do not** have the correct versions of **R** and **RStudio**, please follow the 
<a href="http://umswc.github.io/2016-05-11-RMarkdown/" target="_blank">Setup</a> directions on our course page.  

> 3. Install other R packages necessary for the workshop.

```{r install-directions, eval = FALSE}
## Install the correct packages
install.packages("rmarkdown") # Make cool dynamic documents
install.packages("knitr") # Run R Code Chunks
install.packages("ggplot2") # For plotting
install.packages("DT") # Interactive HTML tables
```

```{r library-packages, eval = TRUE}
## Add these packages to the current session to make sure they load correctly
library("rmarkdown") # Make cool dynamic documents
library("knitr") # Run R Code Chunks
library("ggplot2") # For plotting
library("DT") # Interactive HTML tables
```

> 4. If your packages loaded without any errors, then you are ready for the workshop!  

If there were issues with the above packages please try:  

- Troubleshooting by googling the error  
- Bring the error to the workshop for someone to help you out.  


> Looking forward to the workshop!


