---
title: "Relationship of Car Weight and Gas Efficiency"
author: "Marian L. Schmidt"
date: "May 11, 2016"
output: html_document
---

```{r set-global-options}
knitr::opts_chunk$set(echo = TRUE, 
                      eval = TRUE, 
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE,
                      fig.path = "Figures/",
                      fig.width = 5, 
                      fig.height = 5,
                      fig.align = "center")
```


```{r load-packages}
library(ggplot2)
library(dplyr)
library(DT)
library(plotly)
library(knitr)
```


```{r load-multiplot, eval = TRUE, echo = FALSE}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


```{r single-fig, message = FALSE}
ggplot(mtcars, aes(x = mpg)) + xlab("Miles per Gallon") +
    geom_histogram(bins = 30, fill = "cornflowerblue", color = "black") +
    geom_vline(xintercept=mean(mtcars$mpg), col="red") 
```

```{r many-figs, message = FALSE}
myplots <- list()  # new empty list
for(i in 1:ncol(mtcars)){
  col <- names(mtcars)[i]
  ggp <- ggplot(mtcars, aes_string(x = col)) +
    geom_histogram(bins = 30, fill = "cornflowerblue", color = "black") +
    geom_vline(xintercept = mean(mtcars[[col]]), col = "red") 
  myplots[[i]] <- ggp  # add each plot into plot list
}
multiplot(plotlist = myplots, cols = 4)
```



I predict that there will be a relationship between weight and miles per gallon.  

I will test this by running a linear model with the mtcars dataset is within the R datasets.

```{r mtcars-head}
# What does the data look like?
datatable(mtcars) # Interactive table 
```



# Is there a linear relationship between weight and miles per gallon?
```{r linear-model}
# Is there a relationship between the weight of a car and the miles per gallon?
lm_mpg <- lm(mpg ~ wt, data = mtcars) # Run linear model predicting mpg based on wt
coef_lm_mpg <- coef(summary(lm_mpg)) # Extract coefficients to table 
kable(coef_lm_mpg) # Produce non-interactive table - function in knitr
```

It appears that with a gain in every **1000** pounds that there will be a **decrease** in fuel efficiency by `r abs(coef_lm_mpg[2])` miles per gallon



```{r plotting}
# Plot the relationship between weight and miles per gallon  
plot <- ggplot(mtcars, aes(x = wt, y = mpg)) + geom_point() + # 
  geom_smooth(method = "lm") + theme_bw() + # add linear model and make black and white
  xlab("Weight (1000lbs)") + ylab("Miles per Gallon") # Add axis labels  
plot 
ggplotly(plot) # Make the plot interactive
```

# Is there a relationship between transmission type (automatic vs manual) and miles per gallon?


```{r transmission-ttest-asis, results = "asis"}
mpg_auto <- mtcars[mtcars$am == 0,]$mpg # automatic transmission mileage
mpg_manual <- mtcars[mtcars$am == 1,]$mpg # manual transmission mileage
transmission_ttest <- t.test(mpg_auto, mpg_manual)
transmission_ttest
```



```{r transmission-ttest-markup, results = "markup"}
mpg_auto <- mtcars[mtcars$am == 0,]$mpg # automatic transmission mileage
mpg_manual <- mtcars[mtcars$am == 1,]$mpg # manual transmission mileage
transmission_ttest <- t.test(mpg_auto, mpg_manual)
transmission_ttest
```

```{r }
mpg_auto <- mtcars[mtcars$am == 0,]$mpg # automatic transmission mileage
mpg_manual <- mtcars[mtcars$am == 1,]$mpg # manual transmission mileage
transmission_ttest <- t.test(mpg_auto, mpg_manual)
transmission_ttest
```


