---
title: "Notes from RMarkdown Workshop"
author: "Marian L. Schmidt"
date: "May 11, 2016"
output: 
  html_document: 
    highlight: espresso
    theme: spacelab
    toc: yes
---

```{r global-options}
knitr::opts_chunk$set(echo = TRUE, 
                      eval = TRUE, 
                      message = FALSE,
                      warning = FALSE, 
                      fig.path = "Figures/",
                      fig.width = 12, 
                      fig.height = 8)
```

# Today is great!!

# load packages 
```{r load-packages}
library(knitr)
library(DT)
```


```{r head-mtcars, cache=TRUE}
kable(head(mtcars, n = 4))
datatable(head(mtcars, n = nrow(mtcars)), options = list(pageLength = 5)) 
```



Hello!  **Hello**  __Hello!!__  

*Hello*

<!--This is a comment-->

### I am coding 

[https://www.rstudio.com](https://www.rstudio.com)

1. list
2. list  

> 3. list  

**Chocolate Chip cookie Recipe**  

1. butter  
2. sugar   
    - A mix of brown & white sugar makes it more delicious  
        - mix with butter before you add the eggs  
3. eggs  
4. vanilla
Mix dry ingredients:
flour, salt, baking soda
chocolate chips


I am curious what is 2^11^? It is `r  2^11`.



```{r mean-mpg-mtcars, echo = FALSE, eval = FALSE}  
mean_mpg <- mean(mtcars$mpg)
mean_mpg
```

The average miles per gallon in `mtcars` is `r mean(mtcars$mpg)`.





