---
title: "Creating Dynamic Documents with RMarkdown and Knitr"
author: "Marian L. Schmidt"
date: "May 11th, 2016"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    keep_md: true
    theme: lumen 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Getting Started

# 1. Load Packages
The following packages are necessary for to
```{r load-libraries}
#install.packges("knitr")
library(knitr)
#install.packages("dplyr")
library(dplyr)
#install.packages("ggplot2")
library(ggplot2)
```


# Dynamic Documents  

<a href="https://en.wikipedia.org/wiki/Literate_programming">Literate programming</a> is the basic idea behind dynamic documents and was proposed by Donald Knuth in 1984.  Originally, it was for mixing the source code and documentation of software development together.  Then we could:  

1. **Tangle**:  Extract the source code out of the document.  
2. **Weave**:  Execute the code to get the compiled results.  

In dynamic documents, program or analysis code is run to produce output (e.g. tables, plots, models, etc) and then are explained through narrative writing. 




# RMarkdown

## YAML Headers

### RMarkdown Appearance and Syle
Rmarkdown has several options that control the appearance of HTML documents.  Some aruments to choose from are:  

- **theme**  
- **highlight**  
- **smart**  


The HTML output themes are drawn from the <a href="http://bootswatch.com/">Bootswatch</a> library.  Valid **HTML themes** include the following:    

- `cerulean`, `cosmo`, `default`,`flatly`, `journal`, `lumen`, `paper`, `readable`, `sandstone`, `spacelab`, `simplex`, `united`, and `yeti`.  
    - For example, the theme of this page is `lumen`.
- Pass null for no theme (in this case you can use the css parameter to add your own styles).

**Highlight** specifies the syntax highlighting style. Supported styles include the following:  

- `default`, `espresso`, `haddock`, `kate`, `monochrome`, `pygments`, `tango`, `textmate`, and `zenburn`.   
- Pass null to prevent syntax highlighting.

**Smart** indicates whether to produce typographically correct output, converting straight quotes to curly quotes, --- to em-dashes, -- to en-dashes, and ... to ellipses. **Smart** is enabled by default.

For example:

```
---
output:
  html_document:
    theme: slate
    highlight: tango
---
```

If you felt inclined, you could also produce and use your own theme.  If you did so, the output section of your YAML header would like like:  
```
output:
  html_document:
    css: styles.css
```

If you wanted to go the extra mile and write your own theme in addition to highlight, the YAML header would look like: 
```
---
output:
  html_document:
    theme: null
    highlight: null
    css: styles.css
---
```



Here's a link to learn more about the <a href="http://rmarkdown.rstudio.com/html_document_format.html#appearance_and_style">Appearance and Style</a> in HTML output.

# Knitr Themes
The knitr syntax theme can be adjusted or completely customized.  If you do not prefer the default themes, use the object `knit_theme` to change it.  There are **80 themes** contained within `knitr` and we can view the names of them by `knit_theme$get()`.

What are the first 30 `knitr` themes?

```{r knitr-themes}
head(knit_theme$get(), 30)
```

We can use `knit_theme$set()` to set the theme.  For example, to set the theme to *fruit* we could run the following code:

```{r knitr-fruit-theme}
knit_theme$set("fruit")
```

Here's the link to find your favorite theme of all the <a href="http://animation.r-forge.r-project.org/knitr/">80 knitr highlight themes</a>.



